---
title: "Bioinformática y Estadística 2"
subtitle: "Aplicaciones aeroespaciales"
author: "Evelia Coss"
date: today
categories: ["Semestre 2026-2", "Materia: Bioestadística", "Institución: UNAM"]
keywords: ["probabilidad", "estadística", "transcriptómica", "curso UNAM"]
description: "Curso intensivo con enfoque en análisis transcriptómico y reproducibilidad"
format:
  html:
    other-links:
      - text: NASA Open Data
        href: https://data.nasa.gov/
    code-links:
      - text: Data Import Code
        icon: file-code
        href: "scripts/data-import.py"
---


**Texto con nota al pie:** Este es un ejemplo de nota[^resources-1] que aparecerá como popup.

[^resources-1]: Aquí va el contenido de la nota al pie.

# Code

When you can work @Cannon2014 on your computer and when you need to work on the cluster .. source , RAM, etc. - number of samples?

```{r}
# Notas
a <- 3
b <- 2
suma <- a + b
suma 
```

```{r, eval=FALSE}
InstallData("pbmc3k")
data("pbmc3k")
pbmc3k
```

```{r, eval=FALSE}
library(tidyverse)
library(palmerpenguins)
penguins |>                                      # <1>
  mutate(                                        # <2>
    bill_ratio = bill_depth_mm / bill_length_mm, # <2>
    bill_area  = bill_depth_mm * bill_length_mm  # <2>
  )                                              # <2>
```

1.  Take `penguins`, and then,
2.  add new columns for the bill ratio and bill area.

Comodo de texto

``` text
video-game-sales-r/
├── data/
│   └── vgsales.csv
├── scripts/
│   └── 01_analisis_videojuegos.R
├── figures/
│   ├── grafica_01.png
│   ├── grafica_02.png
│   └── grafica_final.png
├── ejercicio_videojuegos.qmd
└── README.md
```

Python código

``` {python}
import numpy as np
import matplotlib.pyplot as plt

r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(subplot_kw={'projection': 'polar'})
ax.plot(theta, r)
ax.set_rticks([0.5, 1, 1.5, 2])
ax.grid(True)
plt.show()
```


```{python}
#| label: fig-plot
#| fig-cap: "Plot"

import matplotlib.pyplot as plt
plt.plot([1,23,2,4])
plt.show()
```

```{python}
#| label: fig-plots
#| fig-cap: "Plots" 
#| fig-subcap:
#|   - "Plot 1"
#|   - "Plot 2" 
#| layout-ncol: 2

import matplotlib.pyplot as plt
plt.plot([1,23,2,4])
plt.show()

plt.plot([8,65,23,90])
plt.show()
```

For example, see @fig-plot.

See @fig-plots for examples. In particular, @fig-plots-2.



### References

::: {#refs}
:::
